---
title: "Create multiple line chart with R and Plotly"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this post we create some time-series from random data and use the Plotly package to draw a line chart with multiple time-series.


First of all, load Plotly into R using:
```{r, message=FALSE, warning=FALSE}
if(!(require(plotly))){
  install.packages("plotly")
}
require(plotly)
```

Let's generate some random data:

```{r, message=FALSE, warning=FALSE}
n = 50
time <- c(1:n)  
# the R function c() combines elements together, and can be used in to create vectors. 
# In this case it combines the sequence of numbers from 1 to n into a vector.
unifObs <- runif(n)  
normObs <- rnorm(n)
```

```runif(n, min, max)``` function in R draws $n$ random numbers from a Uniform distribution, i.e. $X \sim U[min, max]$. By default, $X \sim U[0, 1]$.

```rnorm(n, mean, sd)``` function draws $n$ realizations from a Normal distribution, with density:

$$f(x) = \dfrac{1}{\sqrt{2\sigma^2 \pi}} e^{-\dfrac{(x-\mu)^2}{2\sigma^2}}$$

By default, $mean = 0$ and $sd = 1$, i.e. $X\sim N(0,1)$.

The ```plot_ly()``` function requires the data to be in a dataframe object, which is a common R data structure.
We create the dataframe passing 3 vectors of the same length to the ```data.frame()``` method:

```{r, message=FALSE, warning=FALSE}
data = data.frame(time,unifObs,normObs)
```

Now we can call the actual ```plot_ly()``` function to create the chart:

```{r, message=FALSE, warning=FALSE}
plot_ly(data, x = ~time, y = ~unifObs, name="uniform",
        type = "scatter", mode = "lines") %>%
  add_trace(y= ~normObs, name="normal", type = "scatter") %>%
  layout(yaxis = list(title = "observations"))
```